Visualizations for the manuscript

### 2022-05-16 metanalysis_visualization/manuscript_Figures.Rmd
coeff label changed to coefficient and feeding and eating disorders now eating disorder
add manually annotation for the sex figure with two pannels, and comment some lines in the one plot only to try add more info to the labels

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.02) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  geom_label(data = plot_annotations_sex_df,
             aes(label = label),
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-08-01'),
           y = 0.69,
           label = "Female proportion", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-08-01'),
           y = 0.3,
           label = "Male proportion", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(title = "Patients sex proportion trends among psychiatric-related visits",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
plot_sex
ggsave(plot = plot_sex, filename = "figure4_ITS_sex.png", height = 15, width = 20, units = "cm")
```

#### Alternative plot 
```{r, include=FALSE}
bootstrapped_fitted_sex %>% 
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

@@

>>>>

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.02) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

plot_sex
ggsave(plot = plot_sex, filename = "figure4_ITS_sex.png", height = 15, width = 20, units = "cm")
```

#### Alternative plot 
```{r, include=FALSE}
plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
                                       sex=c("female", "male"),
                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             #scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df2, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

@@

perc_disorder_group_total$disorder_group <- gsub( "Feeding and Eating Disorders", "Eating Disorders", perc_disorder_group_total$disorder_group)
```
